---
title: "Ukraine manipulation and vote-share models"
output: html_notebook
---

```{r setup}
library(tidyverse)
ukrdata <- read.csv("Ukraine main dataset.csv")

fraudscores <- read.csv("Ukraine fraud scores.csv")

ukrdata <- right_join(ukrdata, fraudscores, by = c("unique.id"))
#ukrdata$region <- relevel(ukrdata$region, ref = "Donetska")
ukrdata$region.group <- relevel(ukrdata$region.group, ref = "West")
ukrdata$president.name <- relevel(as.factor(ukrdata$president.name), ref = "Poroshenko")
ukrdata$east.roz.percent <- ukrdata$e.roz.count.total / ukrdata$n.precincts
ukrdata$west.roz.percent <- ukrdata$w.roz.count.total / ukrdata$n.precincts


```

##Turnout coefficients

Beginning with the causes and effects of turnout coefficients

###Effect of turnout coefficients on party voteshare

```{r turnout coefficients and vote-share, west}
model.west.voteshare <- lm(west.party.voteshare ~ coefs.west + coefs.east +                  over.sixty + loggov + urban.pct + logpop + income.percap + 
                         highered  + presidential.x + orangerev + maidan +                   factor(region.group), data=ukrdata)
summary(model.west.voteshare)

```

```{r turnout coefficients and vote-share, east}
model.east.voteshare <- lm(east.party.voteshare ~ coefs.west + coefs.east +                 over.sixty + loggov + urban.pct + logpop + income.percap + 
                         highered  + presidential.x + orangerev + maidan +                   factor(region.group), data=ukrdata)
summary(model.east.voteshare)
```
Turnout coefficients for both party families are associated with increases in their vote-share.

###Suspiciously high or low coefficients

```{r creating suspicious coef variable}
suspicious.poscoef.west<-matrix(data=NA, nrow=245, ncol=1)
for (i in 1:245){
  ifelse(na.pass(ukrdata$coefs.west[i]) >= 1, suspicious.poscoef.west[i,1]<-1, suspicious.poscoef.west[i,1]<-0)
}

suspicious.negcoef.west<-matrix(data=NA, nrow=245, ncol=1)
for (i in 1:245){
  ifelse(na.pass(ukrdata$coefs.west[i]) < 0 , suspicious.negcoef.west[i,1]<-1, suspicious.negcoef.west[i,1]<-0)
}

suspicious.poscoef.east<-matrix(data=NA, nrow=245, ncol=1)
for (i in 1:245){
  ifelse(na.pass(ukrdata$coefs.east[i])  >=1, suspicious.poscoef.east[i,1]<-1, suspicious.poscoef.east[i,1]<-0)
}

suspicious.negcoef.east<-matrix(data=NA, nrow=245, ncol=1)
for (i in 1:245){
  ifelse(na.pass(ukrdata$coefs.east[i]) < 0 , suspicious.negcoef.east[i,1]<-1, suspicious.negcoef.east[i,1]<-0)
}

ukrdata <- cbind(ukrdata, suspicious.poscoef.west, suspicious.poscoef.east, suspicious.negcoef.east, suspicious.negcoef.west)

```

```{r}
model.west.voteshare.posco <- lm(west.party.voteshare ~ suspicious.poscoef.west  +  suspicious.negcoef.west + suspicious.negcoef.east + suspicious.poscoef.east +                over.sixty + loggov + urban.pct + logpop + income.percap + 
                         highered  + presidential.x + orangerev + maidan +                   factor(region.group), data=ukrdata)
summary(model.west.voteshare.posco)

model.east.voteshare.posco <- lm(east.party.voteshare ~ suspicious.poscoef.west  +  suspicious.negcoef.west + suspicious.negcoef.east + suspicious.poscoef.east +                over.sixty + loggov + urban.pct + logpop + income.percap + 
                         highered  + presidential.x + orangerev + maidan +                   factor(region.group), data=ukrdata)
summary(model.east.voteshare.posco)
```
No effect for suspicious coefficients on vote-shares

##Fraud scores

```{r}
model.east.voteshare.fraud <- lm(east.party.voteshare ~ west.fraud.large + east.fraud.large +                 over.sixty + loggov + urban.pct + logpop + income.percap + 
                         highered  + presidential.x + orangerev + maidan +                   factor(region.group), data=ukrdata)
summary(model.east.voteshare.fraud)

model.west.voteshare.fraud <- lm(west.party.voteshare ~ west.fraud.large + east.fraud.large +                 over.sixty + loggov + urban.pct + logpop + income.percap + 
                         highered  + presidential.x + orangerev + maidan +                   factor(region.group), data=ukrdata)
summary(model.west.voteshare.fraud)
```
No relationship between fraud scores and vote-share, either base variable or fraud.large

##Rozenas scores

```{r}
model.west.voteshare.roz <- lm(west.party.voteshare ~  e.roz.count + w.roz.count + n.precincts + over.sixty + loggov + urban.pct + logpop + income.percap + 
                         highered  + presidential.x + orangerev + maidan +                   factor(region.group), data=ukrdata)
summary(model.west.voteshare.posco)

model.east.voteshare.posco <- lm(east.party.voteshare ~  e.roz.count + w.roz.count + n.precincts + over.sixty + loggov + urban.pct + logpop + income.percap + 
                         highered  + presidential.x + orangerev + maidan +                   factor(region.group), data=ukrdata)
summary(model.east.voteshare.posco)
```
No effects here, either for percent or counts.

