---
title: "Ukraine pistar and delta models"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(interplot)
ukrdata <- read.csv("Ukraine main dataset.csv")

fraudscores <- read.csv("Ukraine fraud scores.csv")

ukrdata <- right_join(ukrdata, fraudscores, by = c("unique.id"))
#ukrdata$region <- relevel(ukrdata$region, ref = "Donetska")
ukrdata$region.group <- relevel(ukrdata$region.group, ref = "West")
ukrdata$president.name <- relevel(as.factor(ukrdata$president.name), ref = "Poroshenko")
ukrdata$east.roz.percent <- ukrdata$e.roz.count.total / ukrdata$n.precincts
ukrdata$west.roz.percent <- ukrdata$w.roz.count.total / ukrdata$n.precincts
```

##Voteshare

First, effects on vote-share if any


```{r vote east ps}
model.east.vote <- lm(east.party.voteshare ~  ps.east +  #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*ps.east ,
                              data=ukrdata)
summary(model.east.vote) 
interplot(model.east.vote, var1="ps.east", var2="party.margin")
```
Pi star and delta both have negative effects on east party vote-share in pro-east regions 

```{r vote west ps}
model.west.vote <- lm(west.party.voteshare ~  d.west +  #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*d.west ,
                              data=ukrdata)
summary(model.west.vote) 
interplot(model.west.vote, var1="d.west", var2="party.margin")
```
West party pi star and delta also have negative relationships with vote-share in pro-west regions.

This may suggest that, after the OR, only smaller kinds of administrative fraud became feasible, and these are carried out by the incumbent administration against their rivals.
Regressions by president are uninformative, since the CIs are too wide (only 1 or 2 elections per president)

However, plotting by party.margin and colored by president seems to suggest that this is plausible

```{r}
p1 <- qplot(party.margin, ps.east, data=ukrdata, color = ukrdata$president.name)
p2 <- qplot(party.margin, d.east, data=ukrdata, color = ukrdata$president.name)
p3 <- qplot(party.margin, ps.west, data=ukrdata, color = ukrdata$president.name)
p4 <- qplot(party.margin, d.west, data=ukrdata, color = ukrdata$president.name)
p1
p2
p3
p4
```



```{r}
model.interaction.west.s <- lm(d.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + region.group,
                              data=ukrdata)
summary(model.interaction.west.s) 
```

##Predictors of fraud measures

###East parties

```{r delta orangerev east}
model.interaction.east.or <- lm(d.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*orangerev ,
                              data=ukrdata)
summary(model.interaction.east.or) 
interplot(model.interaction.east.or, var1="orangerev", var2="party.margin")
```

```{r delta maidan east}
model.interaction.east.m <- lm(d.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*maidan ,
                              data=ukrdata)
summary(model.interaction.east.m) 
interplot(model.interaction.east.m, var1="maidan", var2="party.margin")
```


```{r delta yan east}
model.interaction.east.y <- lm(d.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*yanukovych ,
                              data=ukrdata)
summary(model.interaction.east.y) 
interplot(model.interaction.east.y, var1="yanukovych", var2="party.margin")
```






```{r ps orangerev east}
model.ps.east.or <- lm(ps.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*orangerev ,
                              data=ukrdata)
summary(model.ps.east.or) 
interplot(model.ps.east.or, var1="orangerev", var2="party.margin")
```

```{r ps maidan east}
model.ps.east.m <- lm(ps.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*maidan ,
                              data=ukrdata)
summary(model.ps.east.m) 
interplot(model.ps.east.m, var1="maidan", var2="party.margin")
```


```{r ps yan east}
model.ps.east.y <- lm(ps.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*yanukovych ,
                              data=ukrdata)
summary(model.ps.east.y) 
interplot(model.ps.east.y, var1="yanukovych", var2="party.margin")
```


###West parties


```{r delta orangerev west}
model.interaction.west.or <- lm(d.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*orangerev ,
                              data=ukrdata)
summary(model.interaction.west.or) 
interplot(model.interaction.west.or, var1="orangerev", var2="party.margin")
```

```{r delta maidan west}
model.interaction.west.m <- lm(d.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*maidan ,
                              data=ukrdata)
summary(model.interaction.west.m) 
interplot(model.interaction.west.m, var1="maidan", var2="party.margin")
```


```{r delta yan west}
model.interaction.west.y <- lm(d.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*yanukovych ,
                              data=ukrdata)
summary(model.interaction.west.y) 
interplot(model.interaction.west.y, var1="yanukovych", var2="party.margin")
```






```{r ps orangerev west}
model.ps.west.or <- lm(ps.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*orangerev ,
                              data=ukrdata)
summary(model.ps.west.or) 
interplot(model.ps.west.or, var1="orangerev", var2="party.margin")
```

```{r ps maidan west}
model.ps.west.m <- lm(ps.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*maidan ,
                              data=ukrdata)
summary(model.ps.west.m) 
interplot(model.ps.west.m, var1="maidan", var2="party.margin")
```


```{r ps yan west}
model.ps.west.y <- lm(ps.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*yanukovych ,
                              data=ukrdata)
summary(model.ps.west.y) 
interplot(model.ps.west.y, var1="yanukovych", var2="party.margin")
```


##Overall coefficients

```{r}
model.coef.west.or <- lm(coefs.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*orangerev ,
                              data=ukrdata)
summary(model.coef.west.or) 
interplot(model.coef.west.or, var1="orangerev", var2="party.margin")
```


```{r}
model.coef.west.m <- lm(coefs.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*maidan ,
                              data=ukrdata)
summary(model.coef.west.m) 
interplot(model.coef.west.m, var1="maidan", var2="party.margin")
```

```{r}
model.coef.west.y <- lm(coefs.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*yanukovych ,
                              data=ukrdata)
summary(model.coef.west.y) 
interplot(model.coef.west.y, var1="yanukovych", var2="party.margin")
```





```{r}
model.coef.east.or <- lm(coefs.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*orangerev ,
                              data=ukrdata)
summary(model.coef.east.or) 
interplot(model.coef.east.or, var1="orangerev", var2="party.margin")
```


```{r}
model.coef.east.m <- lm(coefs.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*maidan ,
                              data=ukrdata)
summary(model.coef.east.m) 
interplot(model.coef.east.m, var1="maidan", var2="party.margin")
```

```{r}
model.coef.east.y <- lm(coefs.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + round.2.x
                                 + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ west.approval.margin 
                              +  party.margin*yanukovych ,
                              data=ukrdata)
summary(model.coef.east.y) 
interplot(model.coef.east.y, var1="yanukovych", var2="party.margin")
```

