---
title: "Ukraine manipulation models"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(interplot)
ukrdata <- read.csv("Ukraine main dataset.csv")

fraudscores <- read.csv("Ukraine fraud scores.csv")

ukrdata <- right_join(ukrdata, fraudscores, by = c("unique.id"))
#ukrdata$region <- relevel(ukrdata$region, ref = "Donetska")
ukrdata$region.group <- relevel(ukrdata$region.group, ref = "West")
ukrdata$president.name <- relevel(as.factor(ukrdata$president.name), ref = "Poroshenko")
ukrdata$east.roz.percent <- ukrdata$e.roz.count.total / ukrdata$n.precincts
ukrdata$west.roz.percent <- ukrdata$w.roz.count.total / ukrdata$n.precincts
```

##Predictors of manipulation meausres

Starting with turnout coefficients

###Turnout coefficients

Aim here is to look at how east party plurality affects coefficients during crisis years and the 2012 election (most consolidated under Yanukovych)

```{r orangerev west}
model.interaction.west.s <- lm(coefs.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x + kuchma + poroshenko + orangerev + yanukovych  + maidan  #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*orangerev ,
                              data=ukrdata)
summary(model.interaction.west.s) 
interplot(model.interaction.west.s, var2="orangerev", var1="party.margin")
```

Orange rev increases west party turnout coefficients in pro-west regions; no effect in the East. This is what could be expected given that the revolution did not dismantle eastern networks, but allowed for coordination around Yuschenko.

```{r orangerev east}
model.interaction.east.s <- lmer(coefs.east  ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + kuchma + poroshenko + orangerev + yanukovych    #+ wartime.election
                                + party.margin + #+crisis.year 
                                #+ east.approval.margin 
                                
                                party.margin*orangerev + (1 | regionid),
                              data=ukrdata)
summary(model.interaction.east.s) 

p.orange <- interplot(model.interaction.east.s, var1="orangerev", var2="party.margin", hist=TRUE) + 
  labs(x = "pro-East regional margin of victory", y = "Marginal effect of Orange Revolution") +
  geom_hline(yintercept = 0, linetype = 2) + theme_bw()
p.orange

png("orange-rev turnout coefficient me.png", height=5,
    width=7, units="in", res=600)
p.orange
dev.off()
```

Orange rev has no effect on east party coefficients anywhere

```{r maidan west}
model.interaction.west.maidan <- lmer(coefs.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + kuchma + poroshenko + orangerev + yanukovych  + maidan #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*maidan + (1|regionid),
                              data=ukrdata)
summary(model.interaction.west.maidan) 
interplot(model.interaction.west.maidan, var1="maidan", var2="party.margin")
```

The maidan has no effect on west party coefficients anywhere

```{r maidan east}
model.interaction.east.maidan <- lmer(coefs.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + kuchma + poroshenko +  yanukovych  + maidan #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*maidan + (1|regionid),
                              data=ukrdata)
summary(model.interaction.east.maidan) 
p.maidan <- interplot(model.interaction.east.maidan, var1="maidan", var2="party.margin", hist=TRUE) + 
  labs(x = "pro-East regional margin of victory", y = "Marginal effect of Euromaidan") +
  geom_hline(yintercept = 0, linetype = 2) + theme_bw()
p.maidan
interplot(model.interaction.east.maidan, var2="maidan", var1="party.margin")


png("maidan turnout coefficient me.png", height=5,
    width=7, units="in", res=600)
p.maidan
dev.off()
```

But east party coefficients drop significantly in the east

```{r yanu west}
model.interaction.west.yan <- lm(coefs.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*yanukovych ,
                              data=ukrdata)
summary(model.interaction.west.yan) 
interplot(model.interaction.west.yan, var1="yanukovych", var2="party.margin")
interplot(model.interaction.west.yan, var2="yanukovych", var1="party.margin")

```

Yanukovych has no effect for west party coefficients

```{r yanu east}
model.interaction.east.yan <- lm(coefs.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + orangerev + maidan + yanukovych #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*yanukovych ,
                              data=ukrdata)
summary(model.interaction.east.yan) 
interplot(model.interaction.east.yan, var1="yanukovych", var2="party.margin")
interplot(model.interaction.east.yan, var2="yanukovych", var1="party.margin")

```

Yanukovych increases east party margins across the board
###Period dummies


```{r orangerev west periods}
model.interaction.west.orp <- lm(coefs.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x 
                                 + orangerev + pre.orange.period + post.orange.period + post.maidan.period #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*post.orange.period ,
                              data=ukrdata)
summary(model.interaction.west.orp) 
interplot(model.interaction.west.orp, var1="post.orange.period", var2="party.margin")
interplot(model.interaction.west.orp, var2="post.orange.period", var1="party.margin")

```


```{r orangerev east periods}
model.interaction.east.orp <- lm(coefs.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered + presidential.x 
                                 + orangerev + pre.orange.period + yanukovych.period + post.maidan.period #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                              +  party.margin*post.maidan.period ,
                              data=ukrdata)
summary(model.interaction.east.orp) 
interplot(model.interaction.east.orp, var1="post.maidan.period", var2="party.margin")
interplot(model.interaction.east.orp, var2="post.maidan.period", var1="party.margin")

```

We see a decline in east party coefficients in pro-east regions in the two elections after the Maidan



###Region groups
Now consider turnout coefs using region.group instead of party.margin

```{r regiongroup orangerev west}
model.interaction.west.group.or <- lm(coefs.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + orangerev + maidan #+ wartime.election
                                + region.group #+crisis.year 
                                #+ east.approval.margin 
                              +  region.group*orangerev ,
                              data=ukrdata)
summary(model.interaction.west.group.or) 
#interplot(model.interaction.west.s, var1="orangerev", var2="east.party.plurality")
```

```{r regiongroup orangerev east}
model.interaction.east.group.or <- lm(coefs.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + orangerev + maidan #+ wartime.election
                                + region.group #+crisis.year 
                                #+ east.approval.margin 
                              +  region.group*orangerev ,
                              data=ukrdata)
summary(model.interaction.east.group.or) 
#interplot(model.interaction.west.s, var1="orangerev", var2="east.party.plurality")
```


```{r regiongroup maidan west}
model.interaction.west.group.m <- lm(coefs.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + orangerev + maidan #+ wartime.election
                                + region.group #+crisis.year 
                                #+ east.approval.margin 
                              +  region.group*maidan ,
                              data=ukrdata)
summary(model.interaction.west.group.m) 
#interplot(model.interaction.west.s, var1="orangerev", var2="east.party.plurality")
```

```{r regiongroup maidan east}
model.interaction.east.group.m <- lm(coefs.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + orangerev + maidan #+ wartime.election
                                + region.group #+crisis.year 
                                #+ east.approval.margin 
                              +  region.group*maidan ,
                              data=ukrdata)
summary(model.interaction.east.group.m) 
#interplot(model.interaction.west.s, var1="orangerev", var2="east.party.plurality")
```

```{r regiongroup yan west}
model.interaction.west.group.yan <- lm(coefs.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + orangerev + maidan + yanukovych #+ wartime.election
                                + region.group #+crisis.year 
                                #+ east.approval.margin 
                              +  region.group*yanukovych ,
                              data=ukrdata)
summary(model.interaction.west.group.yan) 
#interplot(model.interaction.west.s, var1="orangerev", var2="east.party.plurality")
```

```{r regiongroup yan east}
model.interaction.east.group.yan <- lm(coefs.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + orangerev + maidan + yanukovych #+ wartime.election
                                + region.group #+crisis.year 
                                #+ east.approval.margin 
                              +  region.group*yanukovych ,
                              data=ukrdata)
summary(model.interaction.east.group.yan) 
#interplot(model.interaction.west.s, var1="orangerev", var2="east.party.plurality")
```

###Suspicious coefs
```{r creating suspicious coef variable}
suspicious.poscoef.west<-matrix(data=NA, nrow=245, ncol=1)
for (i in 1:245){
  ifelse(na.pass(ukrdata$coefs.west[i]) >= 1, suspicious.poscoef.west[i,1]<-1, suspicious.poscoef.west[i,1]<-0)
}

suspicious.negcoef.west<-matrix(data=NA, nrow=245, ncol=1)
for (i in 1:245){
  ifelse(na.pass(ukrdata$coefs.west[i]) < 0 , suspicious.negcoef.west[i,1]<-1, suspicious.negcoef.west[i,1]<-0)
}

suspicious.poscoef.east<-matrix(data=NA, nrow=245, ncol=1)
for (i in 1:245){
  ifelse(na.pass(ukrdata$coefs.east[i])  >=1, suspicious.poscoef.east[i,1]<-1, suspicious.poscoef.east[i,1]<-0)
}

suspicious.negcoef.east<-matrix(data=NA, nrow=245, ncol=1)
for (i in 1:245){
  ifelse(na.pass(ukrdata$coefs.east[i]) < 0 , suspicious.negcoef.east[i,1]<-1, suspicious.negcoef.east[i,1]<-0)
}

ukrdata <- cbind(ukrdata, suspicious.poscoef.west, suspicious.poscoef.east, suspicious.negcoef.east, suspicious.negcoef.west)

```

```{r suspicious coefs west parties}
model.interaction.west.neg <- glm(suspicious.negcoef.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + yanukovych #+ wartime.election
                                + east.party.plurality #+crisis.year 
                                #+ east.approval.margin 
                                +  east.party.plurality*yanukovych,
                             family=binomial(link="logit"), data=ukrdata)
summary(model.interaction.west.neg) 


model.interaction.east.neg <- glm(suspicious.poscoef.west ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + yanukovych #+ wartime.election
                                + east.party.plurality #+crisis.year 
                                #+ east.approval.margin 
                                +  east.party.plurality*yanukovych,
                             family=binomial(link="logit"), data=ukrdata)
summary(model.interaction.east.neg) 
```
No effects for west party suspicious coefs for either orangerev, maidan, or yan


```{r suspicious coefs east parties}
model.interaction.east.neg <- glm(suspicious.negcoef.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x  #+ wartime.election
                                + east.party.plurality #+crisis.year 
                                #+ east.approval.margin 
                                + orangerev + east.party.plurality*orangerev,
                             family=binomial(link="logit"), data=ukrdata)
summary(model.interaction.east.neg) 


model.interaction.east.pos <- glm(suspicious.poscoef.east ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + yanukovych #+ wartime.election
                                + east.party.plurality #+crisis.year 
                                #+ east.approval.margin 
                                +  east.party.plurality*yanukovych,
                             family=binomial(link="logit"), data=ukrdata)
summary(model.interaction.east.pos) 
```

No interaction effects for these suspicious coefficients

###Fraud score

```{r fraud scores west or}
model.interaction.west.fraud.or <- glm(west.fraud.large ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x  #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                                + orangerev + party.margin*orangerev,
                             family=binomial(link="logit"), data=ukrdata)
summary(model.interaction.west.fraud.or) 
interplot(model.interaction.west.fraud.or, var2="party.margin", var1 = "orangerev")
```


```{r fraud scores east or}
model.interaction.east.fraud.or <- glm(east.fraud.large ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x  #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                                + orangerev + party.margin*orangerev,
                             family=binomial(link="logit"), data=ukrdata)
summary(model.interaction.east.fraud.or) 
interplot(model.interaction.east.fraud.or, var2="party.margin", var1 = "orangerev")
```


```{r fraud scores west maid}
model.interaction.west.fraud.m <- glm(west.fraud.large ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x  #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                                + maidan + party.margin*maidan,
                             family=binomial(link="logit"), data=ukrdata)
summary(model.interaction.west.fraud.m) 
interplot(model.interaction.west.fraud.m, var2="party.margin", var1 = "maidan")
```


```{r fraud scores east maid}
model.interaction.east.fraud.m <- glm(east.fraud.large ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x  #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                                + maidan + party.margin*maidan,
                             family=binomial(link="logit"), data=ukrdata)
summary(model.interaction.east.fraud.m) 
interplot(model.interaction.east.fraud.m, var2="party.margin", var1 = "maidan")
```


```{r fraud scores west yan}
model.interaction.west.fraud <- glm(west.fraud.large ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x  #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                                + yanukovych + party.margin*yanukovych,
                             family=binomial(link="logit"), data=ukrdata)
summary(model.interaction.west.fraud) 
interplot(model.interaction.west.fraud, var2="party.margin", var1 = "yanukovych")
```

```{r fraud scores east yan}
model.interaction.east.fraud <- glm(east.fraud.large ~ #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x  #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                                + yanukovych + party.margin*yanukovych,
                             family=binomial(link="logit"), data=ukrdata)
summary(model.interaction.east.fraud) 
```

###Rozenas estimates

```{r rozenas east or}
model.roz.east <- glm(e.roz.count.total ~ n.precincts + #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + orangerev #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                                +  party.margin*orangerev,
                                  family=quasipoisson,
                              data=ukrdata)
summary(model.roz.east)
interplot(model.roz.east, var1="orangerev", var2="party.margin")
```

```{r rozenas west}
model.roz.west <- glm(w.roz.count.total ~ n.precincts +#average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + orangerev #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                                +  party.margin*orangerev
                      , family=quasipoisson ,
                              data=ukrdata)
summary(model.roz.west)
interplot(model.roz.west, var1="orangerev", var2="party.margin")
```


```{r rozenas east maidan}
model.roz.east.m <- glm(e.roz.count.total ~ n.precincts + #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + maidan #+ wartime.election
                                + party.margin #+crisis.year 
                                #+ east.approval.margin 
                                +  party.margin*maidan,
                                  family=quasipoisson,
                              data=ukrdata)
summary(model.roz.east.m)
interplot(model.roz.east.m, var1="maidan", var2="party.margin")
```


```{r rozenas west maidan}
model.roz.west.m <- glm(w.roz.count.total ~ n.precincts + #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + maidan #+ wartime.election
                                + east.party.plurality #+crisis.year 
                                #+ east.approval.margin 
                                +  east.party.plurality*maidan,
                                  family=quasipoisson,
                              data=ukrdata)
summary(model.roz.west.m)
interplot(model.roz.west.m, var1="maidan", var2="east.party.plurality")
```



```{r rozenas east yan}
model.roz.east.y <- glm(e.roz.count.total ~ n.precincts + #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + yanukovych #+ wartime.election
                                + east.party.plurality #+crisis.year 
                                #+ east.approval.margin 
                                +  east.party.plurality*yanukovych,
                                  family=quasipoisson,
                              data=ukrdata)
summary(model.roz.east.y)
interplot(model.roz.east.y, var1="yanukovych", var2="east.party.plurality")
```


```{r rozenas west yan}
model.roz.west.y <- glm(w.roz.count.total ~ n.precincts + #average.wage + 
                                  logold  
                                + loggov #+ edu.employ + health.employ #gov.employ and the other employs are highly cor.
                                +urban.pct + logpop + logincome + ukr.lang.pct + 
                                  highered 
                                + presidential.x + yanukovych #+ wartime.election
                                + east.party.plurality #+crisis.year 
                                #+ east.approval.margin 
                                +  east.party.plurality*yanukovych,
                                  family=quasipoisson,
                              data=ukrdata)
summary(model.roz.west.y)
interplot(model.roz.west.y, var1="yanukovych", var2="east.party.plurality")
```
